Arc Blanc: a real time ocean simulation framework

### 2025-01-17 paper.tex
Change unit and inline equation

To make $P(d)$ and $A(d)$ having the same order of magnitude, the units are the \textbf{decisecond} for performance and the \textbf{meter per seconds} for accuracy (see figure \ref{fig:interpolationCriteria}).
Moreover, the performance being the more important for real-time process, the following arbitrary choice are made for the coefficients of $J$:
\begin{equation}
	\begin{cases}
		\alpha = 1 \\
		\beta = 2
	\end{cases}
\end{equation}

>>>>

To make $P(d)$ and $A(d)$ having the same order of magnitude, the units are the \textbf{seconds} for performance and the \textbf{meter per seconds} for accuracy (see figure \ref{fig:interpolationCriteria}).
Moreover, the performance being the more important for real-time process, the following arbitrary choice are made for the coefficients of $J$: $\alpha = 10$ and $\beta = 2$.
